Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***
```{r Importing data}
pf<-read.csv('pseudo_facebook.tsv',sep='\t')
```

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
library(ggplot2)
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot()+
  stat_summary(fun.y=mean,geom='point',shape=4)
ggplot(aes(x=age,y=friend_count),data=subset(pf,!is.na(gender)))+
  geom_line(aes(color=gender),stat='summary',fun.y=mean)
```

```{r Quiz}
library(dplyr)
grouped_data<-group_by(pf,age,gender)
grouped_data<-filter(grouped_data,!is.na(gender))
pf.fc_by_age_gender<-summarise(grouped_data,
                               mean_friend_count=mean(friend_count),
                               median_friend_count=median(friend_count),
                               n=n())
pf.fc_by_age_gender<-ungroup(pf.fc_by_age_gender)
pf.fc_by_age_gender<-arrange(pf.fc_by_age_gender,age)
pf.fc_by_age_gender
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
ggplot(pf.fc_by_age_gender,aes(y=median_friend_count,x=age))+
  geom_line(aes(color=gender))
```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
library(reshape2)
pf.fc_by_age_gender.wide<-dcast(pf.fc_by_age_gender,
                                age~gender,
                                value.var = 'median_friend_count')
pf.fc_by_age_gender.wide
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(pf.fc_by_age_gender.wide,aes(x=age,y=female/male))+
  geom_hline(yintercept = 1,linetype= 'dashed')+
  geom_line()
```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
pf$year_joined<-floor(2014-pf$tenure/365)
```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
year_joined.bucket<-cut(pf$year_joined,breaks =c(2004,2009,2011,2012,2014))
pf$year_joined.bucket<-year_joined.bucket
table(pf$year_joined.bucket)
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
table(pf$year_joined.bucket,useNA='ifany')
ggplot(aes(x=age,y=friend_count),data=subset(pf,!is.na(gender)))+
  geom_line(aes(color=gender),stat='summary',fun.y=median)
```

```{r Quiz}
table(pf$year_joined.bucket,useNA='ifany')
ggplot(aes(x=age,y=friend_count),data=subset(pf,!is.na(year_joined.bucket)))+
  geom_line(aes(color=year_joined.bucket),stat='summary',fun.y=median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x=age,y=friend_count),data=subset(pf,!is.na(year_joined.bucket)))+
  geom_line(aes(color=year_joined.bucket),stat='summary',fun.y=mean)+
  geom_line(stat='summary',linestyle=2,fun.y=mean)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
summary(subset(pf,tenure>=1)$friend_count/subset(pf,tenure>=1)$tenure)
```

***

### Friendships Initiated
Notes:

What is the median friend rate?
0.2205
What is the maximum friend rate?
417.0000 
```{r Friendships Initiated}
ggplot(aes(x=tenure,y=friendships_initiated/tenure),data=subset(pf,tenure>=1))+
  geom_line(aes(color=year_joined.bucket))
```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

```{r Change line to smooth in our first graph}
ggplot(aes(x=tenure,y=friendships_initiated/tenure),data=subset(pf,tenure>=1))+
  geom_smooth(aes(color=year_joined.bucket))
```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo<-read.csv('yogurt.csv')
yo$id<-factor(yo$id)
```

```{r Quiz}
ggplot(data=yo,aes(x=price))+
  geom_histogram(binwidth = 10)
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
summary(yo)
length(unique(yo$price))
table(yo$price)
```

***
```{r Quiz}
yo<-transform(yo,all.purchases=strawberry+blueberry+pina.colada+plain+mixed.berry)
yo
```

### Prices over Time
Notes:

```{r Prices over Time}
ggplot(data=yo,aes(x=all.purchases))+
  geom_histogram(binwidth = 1)
```

***

```{r Quiz Price X Time}
ggplot(data=yo,aes(x=time,y=price))+
  geom_point()
```

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(4230)
sample.ids<-sample(levels(yo$id),16)

ggplot(aes(x=time,y=price),data=subset(yo,id %in% sample.ids))+
  facet_wrap(~id)+
  geom_line()+
  geom_point(aes(size=all.purchases),pch=1)
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
```{r}
library(GGally)
theme_set(theme_minimal(20))

set.seed(1836)
pf_subset<-pf[,c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset),1000),])
```

Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
library(reshape2)
library(dplyr)
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

