Lesson 3
========================================================

***

### What to Do First?
Notes:
Import the data.
***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf<-read.csv('pseudo_facebook.tsv',sep = '\t')
names(pf)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Importing ggplot2}
library(ggplot2)
```
```{r Histogram of Users\' Birthdays}
qplot(data=pf,x=dob_day,ylab = 'count')+
  scale_x_continuous(breaks=1:31)
```
```{r Another way to plot a Histogram}
ggplot(aes(x=dob_day),data=pf)+
  geom_histogram(binwidth = 1)+
  scale_x_continuous(breaks=1:31)
```

***

#### What are some things that you notice about this histogram?
Response:
Normal because some months we don't have 31 days, thats why day 1 it's really high.
***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:
Some funny videos for my friends.

#### How many of your friends do you think saw that post?
Response:
150

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:
Probably only 30%
***

### Faceting
Notes:

```{r Faceting (Plotting a histogram for each month)}
ggplot(aes(x=dob_day),data=pf)+
  geom_histogram(binwidth = 1)+
  scale_x_continuous(breaks = 1:31)+
  facet_wrap(~dob_month)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:
There's an outlier on the first day of the first month.
***

#### Which case do you think applies to Moira’s outlier?
Response:
A bad data about an extreme case
***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
ggplot(aes(x=friend_count),data=pf)+
  geom_histogram()
```

#### How is this plot similar to Moira's first plot?
Response:
Quite similar.
***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
ggplot(aes(x=friend_count),data=pf)+
  geom_histogram()+
  scale_x_continuous(limits=c(0,1000))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
```{r}
ggplot(aes(x=friend_count),data=pf)+
  scale_x_continuous(limits=c(0,1000),breaks=seq(0,1000,50))+
  geom_histogram(binwidth = 25)
```


### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
ggplot(aes(x=friend_count), data = pf) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))+
  geom_histogram(binwidth = 10)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
ggplot(aes(x=friend_count),data=subset(pf,!is.na(gender)))+
  scale_x_continuous(limits=c(0,1000),breaks=seq(0,1000,50))+
  geom_histogram(binwidth = 25)+
  facet_wrap(~gender)
```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(pf$gender)
by(pf$friend_count,pf$gender,summary)
```

#### Who on average has more friends: men or women?
Response:
Female
#### What's the difference between the median friend count for women and men?
Response:
22
#### Why would the median be a better measure than the mean?
Response:
Because the mean can have outliers
***

### Tenure
Notes:

```{r Tenure}
ggplot(aes(x=tenure),data=pf)+
  geom_histogram(binwidth = 30, color = 'black', fill='#099DD9')
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
ggplot(aes(x=tenure/365),data=pf)+
  geom_histogram(binwidth = .25, color = 'black', fill='#F79420')
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
ggplot(aes(x=tenure/365),data=pf)+
  geom_histogram(color = 'black', fill='#099DD9')+
  scale_x_continuous(breaks = seq(1,7,1), limits = c(0,7))+
  ylab('Number of years using Facebook')+
  xlab('Numbers of users in')
```

***

### User Ages
Notes:

```{r User Ages}
ggplot(aes(x=age),data=pf)+
  geom_histogram(color = 'black', fill='#099DD9',binwidth = 1)+
  scale_x_continuous(breaks = seq(0,113,5))
```

#### What do you notice?
Response:
Most part of the users are between 15 and 30.
***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:
```{r}
summary(pf$friend_count)
summary(log10(pf$friend_count+1))
```
```{r Plotting Friend Count}
p1<-ggplot(data=pf,aes(x=friend_count))+
  geom_histogram()
```

```{r Plotting Friend Count with log10}
p2<-p1+scale_x_log10()
```

```{r Plotting Friend Count with sqrt}
p3<-p1+scale_x_sqrt()
```

```{r Making a grid with the 3 plots above}
library(gridExtra)
grid.arrange(p1,p2,p3,ncol=1)
```


***


### Frequency Polygons

```{r Frequency Polygons}
qplot(x=friend_count,y=..count../sum(..count..),data=subset(pf,!is.na(gender)),
      binwidth=10,geom='freqpoly',color=gender,
      ylab='Proportion of Users with that friend count',
      xlab='Friend Count')+
  scale_x_continuous(limits = c(0,1000),breaks = seq(0,1000,50))
```

```{r}
ggplot(aes(x=www_likes),data=subset(pf,!is.na(gender)))+
  geom_freqpoly(aes(color=gender))+
  scale_x_log10()
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(pf$www_likes,pf$gender,sum)
```


***

### Box Plots
Notes:

```{r Box Plots}
ggplot(data=subset(pf,!is.na(gender)),aes(x=gender,y=friend_count))+
  geom_boxplot()+
  coord_cartesian(ylim=c(0,1000))
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
ggplot(data=subset(pf,!is.na(gender)),aes(x=gender,y=friend_count))+
  geom_boxplot()+
  coord_cartesian(ylim=c(0,1000))
```

***

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
ggplot(data=subset(pf,!is.na(gender)),aes(x=gender,y=friend_count))+
  geom_boxplot()+
  coord_cartesian(ylim=c(0,250))
by(pf$friend_count,pf$gender,summary)
```

Response:
Woman, because the median line it's higher in female boxplot.
***

### Getting Logical
Notes:

```{r Getting Logical}
summary(pf$mobile_likes)
summary(pf$mobile_likes>0)
pf$mobile_check_in<-ifelse(pf$mobile_likes>0,1,0)
pf$mobile_check_in<-factor(pf$mobile_check_in)
summary(pf$mobile_check_in)
```
Q: What percent of check in using mobile?
Response:
```{r}
sum(pf$mobile_check_in==1)/length(pf$mobile_check_in)
```

***

### Analyzing One Variable
Reflection:
Learn that visualization with data it's really important to comunicate what your insights are and how we can take specifics parts of data and see what's going on.
***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!